\mytitle{}

### 2018-10-22 paper/paper.tex
Expansion + Anonymisation

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={\mytitle{}},
	pdfauthor={Kyle A. Simpson, Dimitrios P. Pezaros}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\title{\mytitle{}}
\author{
	Kyle A.\ Simpson\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M508056/1].},
	Dimitrios P.\ Pezaros\\
	University of Glasgow, Glasgow, Scotland,\\
	\email{k.simpson.1@research.gla.ac.uk}
}

@@

Which features might be best suited to this problem?
%?? Relevant features: aggregate network state (load at various points [this has been done, of course]), flow-specific measurements (upload/download ratio when bandwidth above threshold \cite{DBLP:conf/ndss/Rossow14}, packet inter-arrival times, etc.)
?? Relevant features: aggregate network state (load at various points [this has been done, of course]), flow-specific measurements (upload/download ratio when bandwidth above threshold \cite{DBLP:conf/ndss/Rossow14}, packet inter-arrival times, etc.)
%?
%? Need to find a good survey which suggests indicative features.
?? Need to find a good survey which suggests indicative features.
%?? If we assume amplification attacks, we know it won't be `random' source IPs (since it's mostly-legit servers who think that they're doing a good job by replying)
?? If we assume amplification attacks, we know it won't be `random' source IPs (since it's mostly-legit servers who think that they're doing a good job by replying)

@@

?? Oultine attacker's goals, particularly wrt SPIFFY.
?? They want to impact fair-share bandwidth allocation to flows (minimise), they have no worry about being unmasked (there are many available reflectors, which don't need to be bought etc...) [cite the rossow papers about amplification hell].
We assume that attacks are bandwidth-based DDoS attacks with the structure of an \emph{amplification attack}, and that traffic aggregates at the target (unlike in a \emph{transit-link attack}).
The addresses of any machines taking part in an attack are not revealed to the target, save for the fairly stable set of unwitting reflector nodes.

@@

All experiments described were executed using an Ubuntu 16.04.4 LTS machine with a 4-core Intel Core i7-6700K (clocked at \SI{4.2}{\giga\hertz}) and \SI{32}{\gibi\byte} of RAM.
All code underpinning these findings is available on a public repository\footnote{\url{https://github.com/FelixMcFelix/rln-dc-ddos-paper}}.

>>>>

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={\mytitle{}},
%	pdfauthor={Kyle A. Simpson, Dimitrios P. Pezaros}
	pdfauthor={Anonymous Giraffe and Badger}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\title{\mytitle{}}
\author{
%	Kyle A.\ Simpson\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M508056/1].},
%	Dimitrios P.\ Pezaros\\
%	University of Glasgow, Glasgow, Scotland,\\
%	\email{k.simpson.1@research.gla.ac.uk}
Anonymous Giraffe\thanks{This work was supported by a nameless, shapeless funder [grant number 7].},
Anonymous Badger\\
Unnamed Department, Nowhere\\
\email{giraffe.a@unnamed.zoo}
}

@@

%Which features might be best suited to this problem?
%?? Relevant features: aggregate network state (load at various points [this has been done, of course]), flow-specific measurements (upload/download ratio when bandwidth above threshold \cite{DBLP:conf/ndss/Rossow14}, packet inter-arrival times, etc.)
Other studies suggest that there are particularly useful features which make the task of online DDoS flow identification feasible.
Aggregate network load observed at various locations suggests the overall health of a network \cite{DBLP:journals/eaai/MalialisK15}, and the ratio of correspondence between pair flows can suggest asymmetry and in many cases illegitimacy \cite{DBLP:conf/ndss/Rossow14}.
Generic volume-based statistics (counts, counts per duration, average packet sizes) have seen effectiveness in such as $k$-nearest neighbours classifiers \cite{DBLP:conf/dsn/LeeKSPY17}.
Most importantly, there is evidence showing behavioural changes in response to bandwidth expansion \cite{DBLP:conf/ndss/KangGS16}, suggesting similar artefacts might arise after throttling, packet drop, or other interference.
%?? If we assume amplification attacks, we know it won't be `random' source IPs (since it's mostly-legit servers who think that they're doing a good job by replying)
%?? If we assume amplification attacks, we know it won't be `random' source IPs (since it's mostly-legit servers who think that they're doing a good job by replying)

@@

%?? Oultine attacker's goals, particularly wrt SPIFFY.
%?? They want to impact fair-share bandwidth allocation to flows (minimise), they have no worry about being unmasked (there are many available reflectors, which don't need to be bought etc...) [cite the rossow papers about amplification hell].
An attacker's goal is to minimise the fair-share bandwidth allocation that a server can give to any host which connects to it, we they are expected to act rationally in its pursuit.
We assume that attacks are bandwidth-based DDoS attacks with the structure of an \emph{amplification attack}, and that traffic aggregates at the target (unlike in a \emph{transit-link attack}).
The addresses of any machines taking part in an attack are not revealed to the target, save for the fairly stable set of unwitting reflector nodes.
The discovery of any reflector by some defence system does have a cost to the attacker---there is a particularly large (finite) supply of viable reflector nodes \cite{DBLP:conf/ndss/Rossow14}, but the constraints that each has a large upstream bandwidth and support for high-amplification-factor protocols narrow this pool.

@@

All experiments described were executed using an Ubuntu 16.04.4 LTS machine with a 4-core Intel Core i7-6700K (clocked at \SI{4.2}{\giga\hertz}) and \SI{32}{\gibi\byte} of RAM.
All code underpinning these findings is available on a public repository\footnote{\url{https://aweb.site/a-repo.}}.
%All code underpinning these findings is available on a public repository\footnote{\url{https://github.com/FelixMcFelix/rln-dc-ddos-paper}}.
